### 2022-08-05 manuscript.Rmd
Use bonferroni correction for contrasts

  # Compute marginal means and contrasts
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  specs <- pairwise ~ condition | phase
  em <- emmeans(build@model, specs, infer = TRUE)

  # Create list of returns
  list(
    "model" = build@model,
    "summary" = build@summary,
    "anova" = build@anova,
    "means" = em$emmeans,
    "contrasts" = em$contrasts
  ) %>%
    return()
}) %>%
  # Add ERP component names
  set_names(deps) -> models

>>>>

  # Compute marginal means and contrasts
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  specs <- pairwise ~ condition | phase
  means <- emmeans(build@model, specs = c("phase", "condition"))
  contrasts <- contrast(means, "pairwise", simple = "condition") %>%
    summary(by = NULL, adjust = "bonferroni")

  # Create list of returns
  list(
    "model" = build@model,
    "summary" = build@summary,
    "anova" = build@anova,
    "means" = means,
    "contrasts" = contrasts
  ) %>%
    return()
}) %>%
  # Add ERP component names
  set_names(deps) -> models
